On Misuses of the Kolmogorov--Smirnov Test for One-Sample Goodness-of-Fit

### 2023-04-18 manuscript/manuscript.tex
added a power study

>>>>

\begin{table}[ht]
  \label{tab:power}
  \caption{Power of rejecting the null hypothesis of normal and gamma
    distribution at significance level 0.05 when the true distribution was
    $\Gamma(8, 1)$ and $N(8, 8)$, respectively. }
\centering
\begin{tabular}{llrrrr}
  \toprule
  &  & \multicolumn{2}{c}{$H_0:$ normal} &
  \multicolumn{2}{c}{$H_0$: gamma}\\
  \cmidrule(lr){3-4}\cmidrule(lr){5-6}
  Dependence & Method & $n = 100$ & $n = 200$ & $n = 100$ & $n = 200$\\
  \midrule
ARMA & naive & 0.40 & 0.66 & 0.52 & 0.78 \\ 
   & copula & 0.33 & 0.56 & 0.44 & 0.72 \\ 
  AR & naive & 0.41 & 0.66 & 0.46 & 0.70 \\ 
   & copula & 0.26 & 0.45 & 0.31 & 0.54 \\ 
  MA & naive & 0.37 & 0.73 & 0.51 & 0.82 \\ 
   & copula & 0.34 & 0.69 & 0.49 & 0.80 \\ 
   \bottomrule
\end{tabular}
\end{table}

Finally, we report a small study of the power of the one-sample KS test with
unspecified parameters and serially dependent data. Using the three dependence
models characterized by ARMA(1, 1), AR(2), and MA(1), we generated serially
dependent data with marginal distributions $N(8, 8)$ left truncated by zero and
$\Gamma(8, 1)$. Then, for data from $\Gamma(8, 1)$, we tested $H_0$ that the
data has marginally a normal distribution; for data from $N(8, 8)$ left
truncated by zero, we tested $H_0$ that the data has marginally a gamma
distribution;  In both cases, no parameters were specified. Two sample sizes
were considered, $n \in \{100, 200\}$. Table~\ref{tab:power} summarizes the
power of rejecting the null hypothesis at significance level~0.05. The tests
based on a working copula have substantial power in rejecting the null
hypothesis and the power increases as sample size increases. The power from the
naive tests where the serial dependence is discarded, although the unspecified
parameters are accounted for, appear to have higher power than the proposed
tests, but this is not reliable since they do not hold their sizes as
demonstrated in the Figures.
